\documentclass[9pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[left=0.4in,top=0.4in,right=0.4in,bottom=0.4in]{geometry}
\usepackage[T1]{fontenc}

% --- Europass Typography ---
\usepackage{helvet} 
\renewcommand{\familydefault}{\sfdefault} % Official Europass sans-serif font

\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{paracol} 
\usepackage[hidelinks]{hyperref}


% --- FIX: Same line start position ---
\setlength{\parindent}{0pt}

% --- Europass Official Colors ---
\definecolor{europassblue}{RGB}{0, 102, 153}
\definecolor{graytext}{RGB}{102, 102, 102}

\pagestyle{empty}

% --- Styling ---
\titleformat{\section}{\large\bfseries\color{europassblue}\uppercase}{}{0pt}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{6pt}

\setlist[itemize]{leftmargin=12pt, noitemsep, topsep=2pt, parsep=1pt}

\begin{document}

% --- Header ---
\begin{center}
    {\Huge \textbf{\color{europassblue} Junaid Rahman Mokit}} \\
    \vspace{5pt}
    \small \color{graytext} Kishoregonj, Dhaka, Bangladesh \quad | \quad 
    \textbf{\color{black}Email:} \href{mailto:jrmokit03@gmail.com}{jrmokit03@gmail.com} \\
    \small
    \textbf{\color{black}LinkedIn:} \href{https://www.linkedin.com/in/junaid-mokit}{\(\rightarrow\)} \quad | \quad
    \textbf{\color{black}GitHub:} \href{https://github.com/JunaidMokit}{\(\rightarrow\)} \quad | \quad
    \textbf{\color{black}Phone:} +8801743403774
\end{center}

\vspace{5pt}

% Professional Divider Line
\columnseprule=0.4pt
\def\columnseprulecolor{\color{europassblue}}
\columnsep=35pt

\begin{paracol}{2}

% --- LEFT COLUMN ---
\section{Education}

\textit{Bachelor of Science in Computer Science and Engineering (B.Sc. in CSE)} \hfill \textbf{2025} \\
\textbf{United International University} \\
CGPA: \textbf{3.19/4.00} \\
Average Marks: \textbf{80.6\%}

\vspace{8pt}

\textit{Higher Secondary Certificate (HSC), Science} \hfill \textbf{2021} \\
\textbf{Wali Newaz Khan College} \\
GPA: \textbf{4.50/5.00} \\
Average Marks: \textbf{75\%}

\section{Technical Skills}
\textbf{Languages:} C++, Java, JavaScript, Python \\
\textbf{Machine Learning:} Pytorch, Pandas \\
\textbf{Frameworks:} Django, React Native, React JS, Node.js, Express.js \\
\textbf{Database:} MySQL, PostgreSQL, MongoDB, Firebase \\
\textbf{Tools:} Git, Github, Postman

\section{Awards \& Honors}
\textbf{1st Runner Up} \\ System Analysis and Design Lab at UIU Project Show

\vspace{4pt}
\textbf{2nd Runner Up} \\ Final Year Design Project I at UIU Project Show

\vspace{4pt}
\textbf{50\% Scholarship} \\ Academic Excellence Award (Fall 2024)

\vspace{4pt}
\textbf{Rising Star} \\ UIU Computer Club (Fall 2022)

\section{Leadership \& Experience}
\textbf{UIU Computer Club} \\
\textit{Media and Communication Executive} \\
\textit{Oct, 2022 -- Oct, 2023}
\begin{itemize}
    \item Handled club communications and digital media presence.
\end{itemize}

\vspace{8pt}
\textbf{UIU Communication Society} \\
\textit{HR Executive} \\
\textit{June, 2022 -- Sep, 2023}
\begin{itemize}
    \item Managed human resource activities and member coordination.
\end{itemize}

\section{Hobbies}
Learning new things, exploring new devices, and playing football.

\section{Languages}
\textbf{Bengali:} Native \\
\textbf{English:} Fluent

% --- RIGHT COLUMN ---
\switchcolumn

\section{Research \& Publications}
\textbf{1. Plant Disease Recognition from the Perspective of Bangladesh: A Comparative Study} \\
\textit{\small Md Musfiqur Rahman, Md Mahbubur Rahman Tusher, Susmita Roy Rinky, \textbf{Junaid Rahman Mokit}, Sudipa Biswas}
\begin{itemize}
    \item Used Several Types of models to enhance accuracy.
    \item Implementation of ensemble models.
\end{itemize}

\vspace{8pt}
\textbf{2. Smart E-Waste Recycling Using AI and Blockchain: Enabling Sustainable Resource Recovery} \\
\textit{\small Al Imran, Md Koushik Ahmed, Mahin Mahmud, \textbf{Junaid Rahman Mokit}, Redwan Utsab, Md Motaharul Islam}
\begin{itemize}
    \item Include waste management by AI blockchain.
    \item Used several datasets and performed data cleaning.
    \item Enhance accuracy.
\end{itemize}

\vspace{8pt}
\textbf{3. A Reproducible Benchmark for Prompt Injection Vulnerability Assessment in SLMs} \\
\textit{\small Md Musfiqur Rahman, Afsana Mimi Eti,\textbf{Junaid Rahman Mokit}, Sadia Afrin Mou, Soumitro Sarker, Mir Mohammad Shibly}
\begin{itemize}
    \item Explain vulnerability of LLM.
    \item Focus on reducing vulnerability and enhancing accuracy.
\end{itemize}

\section{Projects}
\textbf{SMARTUIU - University Management System} \\
\textit{Role: Software \& DB Engineer} \\
\textit{Tools: React JS, Python, Django, MySQL, Git, Github}
\begin{itemize}
    \item Developed system for student, faculty, and admin.
    \item Implemented role-based access control and optimized database schemas.
    \item \textbf{Achieved 30\% reduction} in query time through indexing.
\end{itemize}

\vspace{10pt}
\textbf{UIU JOB BANK} \\
\textit{Role: Software \& DB Engineer} \\
\textit{Tools: React JS, Python, Django, MySQL, REST API, Git, Github}
\begin{itemize}
    \item Built job portal for internship and full-time opportunities.
    \item Integrated REST APIs for search and application.
    \item Designed interactive dashboard for employers and seekers.
\end{itemize}

\vspace{10pt}
\textbf{Rescue Robot} \\
\textit{Tools: C++, Arduino, Ultrasonic Sensor, Camera Module, Wi-Fi Module, REST API} \\
\textit{Role: Software \& Hardware Integration}
\begin{itemize}
    \item Developed a system to detect human presence in disaster-affected buildings and transmit real-time signals.
    \item Integrated a camera module to capture and send situational images using a REST API.
\end{itemize}

\end{paracol}
\end{document}
